Modelling the Co-evolution of Trade and Culture in Past Societies

### 2015-07-01 article.tex
Change table 2 and 3 order and add p-value of the alpha estimated

In a second step we check if the estimated parameters define effectively a power law that statistically describe the data obtained during the simulation. Using again Kolmogorof-Smirnov statistic we run A number of fictive data points are then generated based on this slope. The final step assess the validity of the regression by comparing the real distribution and the fictive distribution. The table ~\ref{tab:powerLawFit} summarizes the results obtained by this method on all setups used for this work. The first number of each cell represents the mean value of all $\alpha$ parameters obtained (across the 100 runs of one setup). The second number (in parenthesis) represents the mean value of all statistical tests performed on each simulation.

\todo{complete table}
\begin{table}[h]
	\centering
	\begin{tabular}{l|llll}
		Innovation rate &\multicolumn{4}{c}{Number of goods}\\
		      & 1   & 3   &  6 & 9  \\\hline
		0.004 & ??  & ??  & ?? & \\
		0.016 & ??  & ??  & ?? & \\
		0.064 & ??  & ??  & ?? & \\\hline
	\end{tabular}
	\caption{Mean $\alpha$ and p-value for all innovation rate and number of goods studied.}
	\label{tab:powerLawFit}
\end{table}

\todo{Change that to say that we test for differents number of good and it doesn't change}
Additional experiments not presented in this article have shown that the neutral model behaves in the exact same way for two, three and four goods. The value of each good evolves independently and the distribution of values for each good is distributed following the same power law with the same properties than for the experiments performed with one good.

\todo{Change her to says that it's interesting to see that they say it's Power Law for .064 fit correlation test but our KS goodness of fit says no}
It is interesting to analyse the slope of these distributions, to compare them to previous experiments testing the ``neutral hypothesis''.  and their standard deviation is presented in table~\ref{tab:mualpha}. We also present side-by-side the results obtained with the same methodology and for the same parameters in~\cite{bentley_random_2004}.

\begin{table}[h]
	\centering
	\begin{tabular}{ll|llll}
		\multicolumn{2}{r}{Agents Number}&\multicolumn{2}{c}{Our result}&\multicolumn{2}{c}{Bentley et. al. 2004}\\
			&$\mu$ & $\alpha$ & SD&$\alpha$&SD\\\hline
		N = 250	&0.004&1.53&0.03&1.54&0.02\\
			&0.016&1.57&0.02&1.57&0.01\\
			&0.064&1.66&0.01&1.67&0.01\\\hline
		N= 500	&0.004&1.50&0.02&1.53&0.03\\
			&0.016&1.55&0.03&1.61&0.04\\
			&0.064&1.78&0.08&1.81&0.10\\
	\end{tabular}
	\caption{Mean $\alpha$ \& SD are calculate on 100 runs for our results, and 5 runs for Bentley et. al. 2004.}
	\label{tab:mualpha}
\end{table}

@@

>>>>

In a second step we check if the estimated parameters define effectively a power law that statistically describe the data obtained during the simulation. Using again Kolmogorof-Smirnov statistic a number of fictive data points are generated based on the estimated power law. From this bootstrapping method we can then calculate a $p$-value to reject or not the hypothesis $H_0$ that our data can indeed be generated from a power law distribution.

The table~\ref{tab:mualpha} summarizes the results obtained by this method on all setups used for this work with $p$-value computed by bootstrapping 100 fictive power law on each simulation. The value shown in the table are the mean $p$-value computed across 100 simulations. We see that in almost every case the null hypothesis cannot be rejected, which mean that indeed the repartition of the price indeed follows a power law.

%The first number of each cell represents the mean value of all $\alpha$ parameters obtained (across the 100 runs of one setup). The second number (in parenthesis) represents the mean value of all statistical tests performed on each simulation.

\todo{Change the transition here to says that it's interesting to see that they say it's Power Law for .064 fit correlation test but our KS goodness of fit says no}
It is interesting to analyse the slope of these distributions, to compare them to previous experiments testing the ``neutral hypothesis''.  and their standard deviation is presented in table~\ref{tab:mualpha}. We also present side-by-side the results obtained with the same methodology and for the same parameters in~\cite{bentley_random_2004}.

\todo{complete table with final result (here it's just false exemple)}
\begin{table}[h]
	\centering
	\begin{tabular}{ll|ccc}
		\multicolumn{2}{r}{Agents Number}&\multicolumn{2}{c}{Our result}&\multicolumn{1}{c}{Bentley et. al. 2004}\\
			&$\mu$ & $\alpha$ (sd) & $p$-value (sd) &$\alpha$ (sd)\\\hline
		N = 250	&0.004&1.53 (0.03)&0.8 (0.05)&1.54 (0.02)\\
			&0.016&1.57 (0.02)&0.6 (0.05)&1.57 (0.01)\\
			&0.064&1.66 (0.01)&0.0 (0.00)&1.67 (0.01)\\\hline
		N= 500	&0.004&1.50 (0.02)&0.6 (0.05)&1.53 (0.03)\\
			&0.016&1.55 (0.03)&0.3 (0.05)&1.61 (0.04)\\
			&0.064&1.78 (0.08)&0.0 (0.00)&1.81 (0.10)\\
	\end{tabular}
	\caption{Mean $\alpha$ \& SD are calculate on 100 runs for our results, and 5 runs for Bentley et. al. 2004.}
	\label{tab:mualpha}
\end{table}

@@

%\todo{Change that to say that we test for differents number of good and it doesn't change}
%Additional experiments not presented in this article have shown that the neutral model behaves in the exact same way for two, three and four goods. The value of each good evolves independently and the distribution of values for each good is distributed following the same power law with the same properties than for the experiments performed with one good.

Before introducing trading mechanism we run a series of experiment to see how react the system when agents are dealing not only with one good but with many. For all simulation and with all mutation rate the results are the same : when more than one good are exchange the repartition of the prices for each good taken separately are the same and this repartition is in turn the same regardless the number of good exchange.

It means that if we plot the repartition of the price of every goods in a simulation with 9 goods, the 9 curves for each good will be superposed, and if we plot on the same graph the repartition for a simulation with one good, the curve of this simulation will again be superposed with the previous. As the graph is not meaningful, we resume this situation with the table~\ref{tab:multiGoods} where are shown the mean of estimated $\alpha$ between each good for different possible configuration.

\todo{complete table with final result (here it's just false exemple)}
\begin{table}[h]
	\centering
	\begin{tabular}{l|llll}
		Innovation rate &\multicolumn{4}{c}{Number of goods}\\
		      & 1   & 3   &  6 & 9  \\\hline
		0.004 &1.53 (0.03)  &1.53 (0.03)&1.53 (0.03)&1.53 (0.03) \\
		0.016 &1.57 (0.02)  &1.57 (0.02)&1.57 (0.02)&1.57 (0.02) \\
		0.064 &1.66 (0.01)  &1.66 (0.01)&1.66 (0.01)&1.66 (0.01) \\\hline
	\end{tabular}
	\caption{Mean $\alpha$ and standard deviation for all innovation rate and different  of goods. The $\alpha$ given here is the mean $\alpha$ among all goods taken separately and computed over 100 runs with 250 agents.}
	\label{tab:multiGoods}
\end{table}
